\documentclass[a4paper,11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{url}
\usepackage[none]{hyphenat}
% Define a section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

% Set spacing between sections
\titlespacing{\section}{0pt}{*2}{*1}

\begin{document}
	
	%====================
	% Name and Contact Info
	%====================
	\begin{flushleft}
		{\LARGE \textbf{Deepaneesh R V}} \\
		\textbf{Address :} Salem , Tamil Nadu \\
		\textbf{Email :} \url{deepaneesh98@gmail.com}\\
		\textbf{Phone:} 7373468818 \\
		\textbf{LinkedIn:} \url{www.linkedin.com/in/deepaneesh} \\
		\textbf{Github:} \url{https://github.com/Deepaneesh} \\
		\textbf{Web-Resume:} \url{https://deepaneesh.github.io/Web-Resume/} \\
	\end{flushleft}
	
	%====================
	% Objective
	%====================
	\section*{Objective}
	Adaptable and quick-learning professional seeking a role to contribute to a dynamic team with problem-solving skills and effective collaboration.
	
	%====================
	% Education
	%====================
	\section*{Education}
	\noindent
	\textbf{Master of Science in Statistics} \hfill 2023 -- 2025 \\
	Bharathiyar University \\
	PSG College of Arts \& Science , Coimbatore \\
	Percentage: 86.65\% [upto 3rd Semester] \\[0.1mm]
	
	\textbf{Bachelor of Science in Statistics} \hfill 2020 -- 2023 \\
	Bharathiyar University \\
	PSG College of Arts \& Science ,Coimbatore\\
	Percentage : 88.85\% \\[0.01mm]
	
	%====================
	% Work Experience
	%====================
	\section*{Courses \& Certificates}
	\noindent
	\begin{itemize}
		\item \textbf{Descriptive Statistics With R Software } \hfill April-2021\\
		- Percentage: 75\%
		\item \textbf{Linear Regression For Business Statistics} \hfill Aug--2023\\
		-Percentage: 85.22\%
		\item \textbf{R programming } \hfill Dec--2023\\
		-Percentage: 98\%
		\item \textbf{Biostatistics and Design of Experiments} \hfill April--2024 \\
		-Percentage: 72\%
		\item \textbf{Essentials of Data Science with R software -2:\\
			Sampling Theory and Linear Regression Analysis} \hfill May--2024 \\
		-Percentage: 77\%
		\item \textbf{Data Analysis with R Programming} \hfill Aug--2024 \\
		-Percentage: 85\%
		\item \textbf{Python Course for Beginners With Certification:\\ Mastering the Essentials} \hfill Oct--2024 \\
		-Percentage: 82\%
		
	\end{itemize}
	
	
	\section*{Internship}
	\begin{description}
		\item[Company Name:] \textbf{SIMA} (South Indian Mill Association)
		\item[Role:] Data Analyst
		\item[Duration:] July-August 2022 \& july--2024
	\end{description}
	Learned about Data Analysis and its application in Textile industry, for 10days during 
	the month of June 2024 and for 15 days during the month of July 2022
	\newpage
	%====================
	% Projects
	%====================
	\section*{Project}
	
	\noindent
	{\textbf{Statistical Study On Vital reports} \hfill Jan-- 2024 \\}
	\begin{description}
		\item[Abstract:] Analyzing the relationship between age of death for region and gender, and predicting future birth and mortality rates by region.
		\item[Tools:] R programming , SPSS , Jamovi , Excel
		\item[Result:] There is A strong relationship between age of death for region and gender , the birth rate and Mortality rate are slowly increasing in future\\
		\linebreak[2mm]
	\end{description}
	\textbf{Optimizing Diabetes Management : A Predictive Approach to Medication Effectiveness}
	\begin{flushright}
		\hfill Jun-- 2024 \\
	\end{flushright}
	\begin{description}
		\item[Abstract:] This project evaluates the effectiveness of Metformin, Glipizide, and Sitagliptin in managing blood glucose levels in Type 2 Diabetes patients over 8 weeks. Using ARIMA models on synthetic data, it forecasts blood glucose trends, identifies Glipizide as the most effective, and provides model accuracy metrics.
		\item[Tools:] R programming 
		\item[Result:] Our study found Glipizide to be the most effective in reducing blood glucose levels in Type 2 Diabetes patients, with a total reduction of 24.5. The ARIMA model reliably predicted glucose normalization within 10 weeks, with MAE of 6.75 and RMSE of 6.76. This emphasizes the value of data-driven approaches in diabetes management.
		
		
	\end{description}
	\vspace{12pt}
	{\textbf{Bangalore Traffic Prediction} \hfill Sep-- 2024 \\}
	\begin{description}
		\item[Abstract:] This project analyzes Bangalore’s traffic patterns to identify months with the highest traffic volume and predict future trends. It explores the relationship between average speed and congestion levels, showing how weather impacts speed and traffic volume. These insights aim to aid in effective traffic management and planning.
		\item[Tools:] R programming 
		\item[Result:] The analysis shows Bangalore’s traffic volume is highest on Wednesdays and peaks in June. Increased average speed reduces congestion, while adverse weather lowers speed, increasing traffic volume. Without intervention, traffic is expected to rise rapidly, highlighting the need for effective management strategies.
		
		
	\end{description}
	\vspace{12pt}
		\textbf{Enhancing Leukemia Detection With Machine Learning And Statistical Analysis}
		\begin{flushright}
			\hfill Mar-- 2025 \\
		\end{flushright}
	\begin{description}
		\item[Abstract:] This study aims to develop highly optimized statistical and machine learning models for accurate leukemia prediction by fine-tuning hyperparameters through iterative methods. It also seeks to identify the best-performing model based on predictive accuracy and analyze key variables influencing leukemia status using feature importance or model coefficients.
		\item[Tools:] R programming , Jamovi 
		\item[Result:] To reduce leukemia risk and improve early detection, individuals with family history or genetic risk should undergo regular screenings. Lifestyle changes, close monitoring of abnormal WBC counts, and public health awareness can aid prevention. More research is needed on socioeconomic and environmental impacts on leukemia development.
		
		
	\end{description}
	
	\vspace{12pt}
	\textbf{A Statistical And Machine Learning Approach To Early Detection And Affected Area Prediction In Neuromuscular Disorders }
	\begin{flushright}
		\hfill Apr-- 2025 \\
	\end{flushright}
	\begin{description}
		\item[Abstract:] This study aims to explore the interplay between treatment adherence, disease severity, and patient outcomes in neuromuscular disorders. It investigates how clinical and treatment factors influence disease progression and patient strength, while evaluating various machine learning models to identify the most effective one for early-stage diagnosis. The best-performing model will be assessed and validated using ROC and AUC values to predict disease stages and major health issues, supporting more accurate diagnosis and treatment.
		\item[Tools:] R programming , Jamovi , Excel 
		\item[Result:] This study explores how treatment adherence, disease severity, and patient outcomes interact in neuromuscular disorders, emphasizing the need for holistic, personalized care. It highlights the power of machine learning models like CatBoost and Random Forest to improve early detection, predict major health issues, and optimize treatment strategies. The findings stress the importance of continuous monitoring, tailored interventions, and further model validation to enhance long-term patient outcomes.
		
		
		
	\end{description}
	%====================
	% Skills
	%====================
	\section*{Skills}
	\begin{itemize}
		\item \textbf{Programming Languages:}  R, Python, SQL
		\item \textbf{Tools and Software:} Excel, MS-Office,
		R-Studio, SPSS, SYSTAT, Jamovi, \LaTeX
		\item \textbf{Version Control:} Git \& Git-hub
		
	\end{itemize}
	
	
	%====================
	% Awards and Achievements
	%====================
	\section*{Awards and Achievements}
	\noindent
	\begin{itemize}
		\item 
		\textbf{BASIC LIFE SUPPORT AND RECOVERY POSITION} \hfill 2023 \\
		-Voluntary work in the 'WORLD RECORD EVENT UNDER \\ ASIA BOOK OF RECORDS'
		\item  Participated in Nova Nordisk \\ Symposium for Innovative and Applied Statistics \hfill June--2024 \& july--2024
	\end{itemize} 
	%====================
	% References
	%====================
	\section*{Interested Area}
	\begin{itemize}
		\item Analysis 
		\item Estimation 
	\end{itemize}
	\section*{Languages Known}
	\begin{itemize}
		\item Tamil 
		\item English 
		\item French
		
	\end{itemize}
	\section*{Hobbies}
	\begin{itemize}
		\item Story Editing
		\item Chess
	\end{itemize}
\end{document}
